---
title: "Exercise 3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Simon Gerloff (12565643)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1
### d)

Strengths and weaknesses of git:

Strengths: 
Using git it is very hard to lose files. Git allows you to go back in the commits and allows you to understand changes that were made

Weaknesses: 
Git can be very complicated for beginners. Saving the history of the files takes up space on the computer.

## Exercise 2
### a)

https://github.com/z4imon/exeRcise-sheet-3.git

## Exercise 3
### b)

```{r}

library(readr)

year2022 <- read_csv("data/open_data_portal_2022.csv")
year2023 <- read_csv("data/vornamen-muenchen-2023.csv")

typeAnzahl2022 <- class("year2022.Anzahl")
typeAnzahl2023 <- class("year2023.Anzahl")

year2022$Anzahl <- gsub("4 oder weniger", "4", year2022$Anzahl)
year2023$Anzahl <- gsub("4 oder weniger", "4", year2023$Anzahl)

year2022$Anzahl <- as.numeric(year2022$Anzahl)
year2023$Anzahl <- as.numeric(year2023$Anzahl)

```
Converted the column "Anzahl" to numeric, some values have been changed from "4 oder weniger" to "4" to be able to convert the value to a numeric data type.

### c)
```{r}

babysBorn2022 <- sum(year2022$Anzahl)
babysBorn2023 <- sum(year2023$Anzahl)

```

In the year of 2022 more babys were born in the year 2023.

### d)
```{r}

year2022$year <- 2022
year2023$year <- 2023

```

### e)
```{r}

library(dplyr)

combined <- bind_rows(year2022, year2023)

```


### f)
```{r}

combinedNames <- combined %>% 
  group_by(Vorname) %>% 
  summarise(Anzahl = sum(Anzahl)) %>% 
  arrange(desc(Anzahl)) %>% 
  head(10)

knitr::kable(combinedNames, caption = "The most popular child names in 2022 and 2023")

```

## Exercise 4
### c)
Used dataset "Global child mortality (since 1800) - based on Gapminder and World Bank (2019).csv" from https://github.com/owid/owid-datasets/blob/master/datasets/Global%20child%20mortality%20(since%201800)%20-%20based%20on%20Gapminder%20and%20World%20Bank%20(2019)/Global%20child%20mortality%20(since%201800)%20-%20based%20on%20Gapminder%20and%20World%20Bank%20(2019).csv

### d)
How much does the child mortality decline per year?

```{r}

childMortality <- read_csv("data/Global child mortality (since 1800) - based on Gapminder and World Bank (2019).csv")

```

### e)
```{r}

childMortality1800 <- childMortality %>% filter(Year == 1800)
childMortality1800 <- childMortality1800$`Share dying in first 5 years (based on Gapminder and World Bank (2019))`

childMortality2017 <- childMortality %>% filter(Year == 2017)
childMortality2017 <- childMortality2017$`Share dying in first 5 years (based on Gapminder and World Bank (2019))`

declinePerYear <- (childMortality1800 - childMortality2017) / (2017 - 1800)

```

The child mortality declines by 0.181520737327189 per year.


