---
title: "Exercise 3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Simon Gerloff (12565643)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1
### d)

Strengths and weaknesses of git:

Strengths: 
Using git it is very hard to lose files. Git allows you to go back in the commits and allows you to understand changes that were made

Weaknesses: 
Git can be very complicated for beginners. Saving the history of the files takes up space on the computer.

## Exercise 2
### a)

https://github.com/z4imon/exeRcise-sheet-3.git

## Exercise 3
### b)

```{r}

library(readr)

year2022 <- read_csv("data/open_data_portal_2022.csv")
year2023 <- read_csv("data/vornamen-muenchen-2023.csv")

typeAnzahl2022 <- class("year2022.Anzahl")
typeAnzahl2023 <- class("year2023.Anzahl")

year2022$Anzahl <- gsub("4 oder weniger", "4", year2022$Anzahl)
year2023$Anzahl <- gsub("4 oder weniger", "4", year2023$Anzahl)

year2022$Anzahl <- as.numeric(year2022$Anzahl)
year2023$Anzahl <- as.numeric(year2023$Anzahl)

```
Converted the column "Anzahl" to numeric, some values have been changed from "4 oder weniger" to "4" to be able to convert the value to a numeric data type.

### c)
```{r}

babysBorn2022 <- sum(year2022$Anzahl)
babysBorn2023 <- sum(year2023$Anzahl)

```

In the year of 2022 more babys were born in the year 2023.

### d)
```{r}

year2022$year <- 2022
year2023$year <- 2023

```

